MINOS Handover Plots

### 2024-04-08 minos/validation/handovers.Rmd
Got council tax working again with some plots in handovers to check it

out.path <- here::here('output', 'glasgow_scaled/')
#out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
```

@@

>>>>

#out.path <- here::here('output', 'glasgow_scaled/')
out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
```

@@

## Max Age

```{r}
raw.maxAge <- raw.dat %>%
  group_by(time) %>%
  summarise(max_age = max(age))

base.maxAge <- base.dat %>%
  group_by(time) %>%
  summarise(max_age = max(age))

handover_lineplots(raw.maxAge, base.maxAge, 'max_age')
```
